Red Oak: Proactive Policy Generation

### 2015-05-09 draft.tex
decision tree image placeholder
small pass on the intro

One of the major outcomes of the Software Defined Networking (SDN) movement, has been that of a unified, open interface to the switch hardware. This has, in turn, enabled new opportunities for network programmability. The typical model for SDN is that of a centralized controller, or distributed set of controllers, programming the switches dynamically to implement the desired control functionality.
However the questions remains as to how best to write programs for SDNs.

Recent collaborations between researches in networking and programming languages have resulting in a number of new, network-specific programming languages. One example is the Frenetic family of languages \cite{Frenetic}, which allow programmers to write simple packet processing functions in a domain-specific language and combine them together using policy combinators. Another approach given in Maple \cite{Maple} is to allow programmers to write policies in an arbitrary, high-level programming language as a function that takes a packet and produces a forwarding path, the algorithmic policy. Conceptually, the function in run anew on each packet that enters the network.

Ultimately, the performance requirements of networks dictate that the centralized controller(s) can not handle most traffic since redirecting packets to be handled by the controller incurs orders of magnitude increased latency. For this reason, compiler technologies for network programming languages must be able to push much of the control plane functionality into the data plane switches themselves.

@@

\begin{enumerate}
\item We describe a static analysis on the user-defined forwarding policy that pushes symbolic packets through the function to explore all possible paths of execution. This analysis is then used to proactively generate forwarding rules to install in the network.
\item We provide a packet API that lets programmers ask if a field is in a particular range (e.g., IP prefix) rather than if the the field equals a particular value. This more expressive test works together with our analysis to better capture programmer intent when setting up forwarding decision in the data plane.
\item We provide a relation/table data structure in our API to maintain global state. The data structure works together with our analysis to provide an automatic invalidation scheme. The analysis determines which future packets might affect global state and ensures that these relevant packets are actually seen by the controller.
\end{enumerate}

@@

  \begin{figure}[ht]

\caption{Decision Tree for Stateful Firewall}     
\label{fig:decisiontree}  
  \end{figure}

@@

   % Can represent constraints on the ranges admissible given a certain topology as a series of ``true'' branches at the root of the tree.

>>>>

One of the major outcomes of the Software Defined Networking (SDN) movement has been a unified, open interface to the switch hardware. This has, in turn, enabled new opportunities for network programmability. The typical model for SDN involves a centralized controller or distributed set of controllers programming switches dynamically to implement the desired control functionality.
However, the questions remains as to how best to write programs for SDNs.

Recent collaborations between researchers in networking and programming languages have resulting in a number of new network-specific programming languages. One example is the Frenetic family of languages \cite{Frenetic}, which allow programmers to write simple packet processing functions in a domain-specific language and combine them together using policy combinators. Another approach, described in Maple \cite{Maple}, is to allow programmers to write policies in an arbitrary, high-level programming language as a function that takes a packet and produces a forwarding path, the algorithmic policy. Conceptually, the function is run anew on each packet that enters the network.

Ultimately, the performance requirements of networks dictate that the centralized controller(s) can not handle most traffic since redirecting packets to be handled by the controller incurs orders of magnitude increased latency compared to those being handled by switches. For this reason, compiler technologies for network programming languages must be able to push much of the control plane functionality into the data plane switches themselves.

@@

\begin{enumerate}
\item We describe a static analysis on the user-defined forwarding policy that pushes symbolic packets through the function to explore all possible paths of execution. This analysis is then used to proactively generate forwarding rules to install in the network.
\item We provide a packet API that lets programmers ask if a field is in a particular range (e.g., IP prefix) rather than if the the field equals a particular value. This more expressive test works together with our analysis to better capture programmer intent when setting up forwarding decision in the data plane.
\item We provide a mutable relation data structure in our API to maintain global state. The data structure works together with our analysis to provide an automatic invalidation scheme. The analysis determines which future packets might affect global state and ensures that these relevant packets are actually seen by the controller.
\end{enumerate}

@@

\begin{figure}[ht]
\includegraphics[scale=.5]{img/dtree.png}
\caption{Decision Tree for Stateful Firewall}     
\label{fig:decisiontree}  
  \end{figure}

@@

   % Can represent constraints on the ranges admissible given a certain topology as a series of ``true'' branches at the root of the tree.
im
